---
title: "BDS Toolbox: DV Assignment 1"
author: "Your Name Here"
date: "`r Sys.Date()`"
output: html_document
---

<!--
HOW TO KNIT THIS FILE

1. Save this file in an `assignment-1/` folder inside your group project
   (next to `scripts/` and `report/`), and open the project in RStudio
   (the `Project:` button in the top right should show your repo name).
2. Click the `Knit` button at the top of this file (or press
   Ctrl/Cmd + Shift + K). An .html file with the same name appears next to
   this .Rmd.
3. Knitting starts from a clean R session: it only knows what is created
   *in this file*. The setup chunk below sources scripts/00-packages.R and
   scripts/01-get-data.R, so packages and data are always loaded. The first
   knit downloads the data, so you need an internet connection.

If knitting fails:
- "could not find function": the package isn't loaded - add it to
  scripts/00-packages.R.
- "object not found": you created it in the Console, not in this file.
- "cannot open file": check that the project is open, and that this file is
  in assignment-1/.
- Check that all code chunks have unique labels.
- Google the error message you receive, as it often provides clues about
  what went wrong.

This comment does not show up in the knitted .html, so you can leave it here.
-->

Use this template to help you get started with your assignment. You can add more code chunks as needed. Submit both documents (.Rmd and .html) following the instructions on the assignment.

**If you make more than one visualization per part, please indicate clearly which visualization we should look at when grading**.

## Setup environment
```{r setup}
knitr::opts_chunk$set(echo = TRUE) # set default echo = TRUE for all code blocks
rm(list = ls()) # Remove any existing objects in memory

# installs (if missing) and loads every package - add any new packages to
# scripts/00-packages.R, not here
source("../scripts/00-packages.R")

# downloads the data into data/raw/ if you don't already have it, then loads
# eindscores, referentieniveaus, schooladviezen and schoolweging
source(here("scripts", "01-get-data.R"))
```

## Part A: Replicate this plot
### Prepare data

```{r data-prep-1}
```

*... add more code chunks as needed. *

### Create plot
```{r plot-1}
```


## Part B: Interactive visualizations with plotly
### Prepare data

```{r data-prep-2}
```

### Create interactive plot

```{r plot-2}
```
